On the Alfvenicity of solar wind discontinuities

### 2024-12-06 article.qmd
feat: update fig-vRatios
update

The multifluid model developed above is used here to study a specific example and the effects of model parameters: assume a density profile for one species taking the form of a Lorentzian function with a background density.

@@

@@

<!-- ::: {.column-page} -->
::: {#fig-vRatios layout-nrow="1" }
![](figures/vRatios.svg){#fig-vRatiosEx1}

![](figures/vRatiosEx2.svg){#fig-vRatiosEx2}

Asymptotic velocity for each species, bulk velocity and normalized one by Alfvén velocity for the case of $u_{1,z} = - u_{2,z}$ (a) and $u_{1,z} = - 2 u_{2,z}$ (b).
:::
<!-- ::: -->

>>>>

The multifluid model developed above is used here to study a specific example and the effects of model parameters. We assume a density profile for the first ion species ($n_1$) that takes the form of a Lorentzian function with a background density:

@@

where $n_1(∞)$ is the asymptotic (background) density far from the current sheet, $κ$ is a dimensionless parameter controlling the peak density enhancement, and $L$ is the characteristic width of the current sheet.

@@

::: {#fig-vRatios layout-nrow="1" }
![](figures/vRatios.pdf){#fig-vRatiosEx1}

![](figures/vRatiosEx2.pdf){#fig-vRatiosEx2}

Asymptotic velocity for each species, bulk velocity and normalized one by Alfvén velocity for the case of $u_{1,z} = - u_{2,z}$ (a) and $u_{1,z} = - 2 u_{2,z}$ (b).
:::
